Extending Camellia for Distributed Stiffness Matrix Determination in DPG

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added experimental setup
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@101 36274a68-8941-4c93-80ef-affaed5139da

Currently, Reftree has been implemented and tested on local clusters. However, Reftree currently crashes during runs on Lonestar, our HPC architecture for this report. We use the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.

@@

\begin{itemize}
\item Describe experimental setup

\item Handicaps - batch cache size, using all 12 cores on a single node

\item

\end{itemize}

\begin{figure}
\centering
\subfigure[Cyclic]{
\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
}
\subfigure[HSFC]{
\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
}
\end{figure}

>>>>

Currently, Reftree has been implemented and tested on local clusters. However, Reftree currently crashes during runs on our HPC architecture for this report. We use the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.

@@

We tested the scalability of our code on the Lonestar machine at the Texas Advanced Computing Center (TACC), verifying whether or not we observe strong/weak scaling for various parts of the program.  We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the North and East edges of the square.  We set up our computational experiments by first refining all cells that share an edge with the North and East sides, and repeating this process four times.   We then construct three additional meshes, by uniformly refining every element in the mesh (quadrupling the number of elements each time).  For each of these meshes, we solve on Longhorn, using 1, 4, 16, and 64 nodes, tracking the timing of various portions of the code.  From this data, we extract strong and weak scaling statistics.

It's worth noting that the runtimes reported here do not represent Camellia running at peak efficiency.  A single Longhorn node contains 12 cores.  Our experiments here request only one core per node; utilizing all 12 cores on a node would decrease communication costs, as well as allow us to more fully take advantage of the multi-threaded linear algebra libraries used by Trilinos.  Additionally, there is a parameter within Camellia that controls the batch size for the Trilinos Intrepid batching routines.  Tuning this parameter based on machine-specific cache sizes should further optimize performance.
